---
title: "Conference Programme"
execute:
  echo: false
  error: false
  warning: false
  message: false
---
Event information posted here is subject to change depending on the requirements of the conference. If changes do occur, we will email all attendees, and disruption to talk times will be minimised. 
```{r}
library(tidyverse)
library(knitr)
library(gt)

submissions = read_csv("./sessions.csv") |> select(
    firstname, lastname, title, session, session_no, room, day, chair, status
) |> mutate(
    date = case_when(
        day==1 ~ "Wednesday, April 23",
        day==2 ~ "Thursday, April 24",
        day==3 ~ "Friday, April 25"
    ),
    time = case_when(
        session_no == 1 ~ "14:30 - 15:30",
        session_no == 2 ~ "15:45 - 16:45",
        session_no == 3 ~ "09:30 - 10:30",
        session_no == 4 ~ "11:00 - 12:00",
        session_no == 5 ~ "14:30 - 15:30",
        session_no == 6 ~ "15:45 - 16:45",
        session_no == 7 ~ "09:00 - 10:00"
    )
)

sessions <- submissions |> filter(!is.na(chair)) |> select(session, session_no, room, date, time, chair) |> rename(start_time='time') |> arrange(desc(date), start_time)


talks <- submissions |> filter(status == "Accepted: Talk") |> 
    mutate(
        session_start_time = 
            lubridate::hm(str_split_i(time, pattern=' - ', 1)) + 
            lubridate::date("2025-04-22") + 
            lubridate::days(day),

    ) |> group_by(session) |> mutate(
        talk_start_time = force_tz(session_start_time + lubridate::minutes(20)*(row_number()-1), 'Europe/London')
    ) |> mutate(
        time = strftime(talk_start_time, "%H:%M")
    ) |> select(- chair) |> left_join(sessions |> select(session, chair), by='session') |> select(
        firstname, lastname, title, session, session_no, date, room, time)

gt_bolden = function(g){
            lapply(g, function(x){gt::md(paste0("**", x, "**"))})
        }

posters <- submissions |> filter(is.na(session)) |> select(-session, -session_no, -room, -day, -chair, -date)

```

# Programme at a glance
Unless otherwise stated, all rooms are in the [Old Engineering Building (Y3)](../venue). 

```{r}

glance_main = read_csv("./at_a_glance.csv")
glance_ecr = read_csv("./ecr.csv") |> mutate(Date = "Tuesday") |> select(-notes)
colnames(glance_ecr) = colnames(glance_main)
rbind(glance_ecr, glance_main) |> 
    select(-`...1`) |> group_by(Date) |> gt() |> 
    gt::text_transform(
        locations=cells_row_groups(),
        fn=gt_bolden
    ) |> cols_label(
        Event = md("**Event**"),
        Time = md("**Time**"),
        Location = md("**Room**")
    )
```

# All Sessions
```{r}
parallel_sessions <- read_csv("./parallel_sessions.csv") |>
  mutate(session_group = paste("Group", session_group))

parallel_sessions |>
  group_by(session_group, date, start_time) |>
  gt() |>
  gt::text_transform(
    locations = cells_row_groups(),
    fn = gt_bolden
  ) |>
  cols_label(
    session = md("**Session**"),
    room = md("**Room**")
    # chair = md("**Chair**")
  )
```

# All Talks
GISRUK 2026 Proceedings on Zenodo - you can find all of the proceedings for the talks and posters available on the GISRUK 2026 community on Zenodo [link](https://zenodo.org/communities/gisruk2026/records?q=&l=list&p=1&s=100&sort=newest). All papers will be added to Zenodo before the start of the conference. Please check the Zenodo link regularly for updates.
```{r}
talks_tbl <- read_csv("./all_talks.csv") |>
  mutate(
    session_group  = paste("Session", session_group),
    session_header = paste0(session_code, ": ", session_title),
    speaker        = paste(firstname, lastname),

    # Create markdown link: [Title](DOI)
    title_with_link = case_when(
      is.na(DOI) | DOI == "" ~ title,                     # no DOI → plain title
      TRUE ~ paste0("[", title, "](", DOI, ")")           # DOI present → hyperlink
    )
  ) |>
  arrange(session_group, session_code)

talks_tbl |>
  select(session_group, session_header, speaker, title_with_link) |>
  gt(groupname_col = "session_group") |>
  cols_label(
    session_header   = md("**Parallel Session**"),
    speaker          = md("**Speaker**"),
    title_with_link  = md("**Talk Title**")
  ) |>
  fmt_markdown(columns = title_with_link) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()
  )
```
# All Posters
GISRUK 2026 Proceedings on Zenodo - you can find all of the proceedings for the talks and posters available on the GISRUK 2026 community on Zenodo [link](https://zenodo.org/communities/gisruk2026/records?q=&l=list&p=1&s=100&sort=newest). All papers will be added to Zenodo before the start of the conference. Please check the Zenodo link regularly for updates. 
```{r}
posters_tbl <- read_csv("./posters.csv") |>
  mutate(
    Session = case_when(
      Session == "AM" ~ "AM Session",
      Session == "PM" ~ "PM Session",
      TRUE ~ Session
    ),
    speaker = paste(firstname, lastname)
  ) |>
  arrange(Session, lastname, firstname)

posters_tbl |>
  select(Session, speaker, Title) |>
  gt(groupname_col = "Session") |>
  cols_label(
    speaker = md("**Speaker**"),
    Title = md("**Poster Title**")
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()
  )

```

# Conference Dinner 
The Conference will be held at [The Exchange](https://www.birmingham.ac.uk/the-exchange/), a University of Birmingham building located in central Birmingham. The meal has been designed to celebrate the [Helios Exhibition](https://www.birmingham.ac.uk/the-exchange/events/helios) that opened in March 2026.

7.00 pm – Arrivals

7.30 pm – Start of food service

The three courses will last around 90 minutes to two hours. Drinks are not included within the meal, but there is a pay as you go bar.

Dress code is smart casual / business casual.
