---
title: "Conference Programme"
execute:
  echo: false
  error: false
  warning: false
  message: false
---
Event information posted here is subject to change depending on the requirements of the conference. If changes do occur, we will email all attendees, and disruption to talk times will be minimized. 
```{r}
library(tidyverse)
library(knitr)
library(gt)

```

# Program at a glance
Unless otherwise stated, all rooms are in the [Old Engineering Building (Y3)](../venue). 

```{r}

glance_main = read_csv("./at_a_glance.csv")
glance_ecr = read_csv("./ecr.csv") |> mutate(Date = "Tuesday (still to confirm)") |> select(-notes)
colnames(glance_ecr) = colnames(glance_main)
rbind(glance_ecr, glance_main) |> 
    select(-`...1`) |> group_by(Date) |> gt() |> 
    gt::text_transform(
        locations=cells_row_groups(),
        fn=gt_bolden
    ) |> cols_label(
        Event = md("**Event**"),
        Time = md("**Time**"),
        Location = md("**Room**")
    )
```

# All Sessions
```{r}
parallel_sessions <- read_csv("./parallel_sessions.csv") |>
  mutate(session_group = paste("Group", session_group))

parallel_sessions |>
  group_by(session_group, date, start_time) |>
  gt() |>
  gt::text_transform(
    locations = cells_row_groups(),
    fn = gt_bolden
  ) |>
  cols_label(
    session = md("**Session**")
    # room = md("**Room**"),
    # chair = md("**Chair**")
  )
```

# All Talks

```{r}
all_talks <- read_csv("./all_talks.csv") |>
  mutate(
    session_group = paste("Session", session_group),
    session_header = paste0(session_code, ": ", session_title),
    author = paste(firstname, lastname)
  )

all_talks |>
  select(session_group, session_header, author, title) |>
  arrange(session_group, session_header) |>
  gt(groupname_col = "session_header", rowname_col = "author") |>
  tab_stubhead(label = md("**Author**")) |>
  cols_label(
    title = md("**Talk Title**")
  )

```
# Conference Dinner 
The Conference will be held at [The Exchange](https://www.birmingham.ac.uk/the-exchange/), a University of Birmingham building located in central Birmingham. The meal has been designed to celebrate the [Helios Exhibition](https://www.birmingham.ac.uk/the-exchange/events/helios) that opened in March 2026.

7.00 pm – Arrivals

7.30 pm – Start of food service

The three courses will last around 90 minutes to two hours. Drinks are not included within the meal, but there is a pay as you go bar.

Dress code is smart casual / business casual.
